Simulation Study: Informative Covariate (sine)

### 2018-06-07 datasets/simulations/simulations-informative-sine.Rmd
Fix typo in results file name

## intermediary files we create below
gauss_file <- file.path(resdir, "informative-sine-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "informative-sine-benchmark-t5.rds")
tdist11_file <- file.path(resdir, "informative-cubic-benchmark-t11.rds")
chisq_file <- file.path(resdir, "informative-sine-benchmark-chisq4.rds")

>>>>

## intermediary files we create below
gauss_file <- file.path(resdir, "informative-sine-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "informative-sine-benchmark-t5.rds")
tdist11_file <- file.path(resdir, "informative-sine-benchmark-t11.rds")
chisq_file <- file.path(resdir, "informative-sine-benchmark-chisq4.rds")
